---
title: "Final Q2"
author: "Abel Meza"
date: "11/26/2019"
output: html_document
---

```{r}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
avastf <- filter(avast,sex=="gal")
```



## QUESTION 2 (Women)

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

In question 2 our goal is to determine how the AID preventive drug should be working with respect to the sex of the women. 

 \(H_0\):There is no difference in the AID preventive drug that is independent to the sex of women.

\(H_A\):There is a statistical difference between AID preventive drug  and to those independent to the sex of the women. 




## Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

We will be using both graphical descriptive and numerical descriptive results with data from only the female.

##Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->


### Descriptive Results


#### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

We use bar charts to compare Numerical vs Numerical data.

```{r}
barchartGC(~infected + treatment,data=avastf)
barchartGC(~infected + treatment,data=avastf,type="percent")
```
In this barchart we can see that about 30% or close to 250 of the females who got AIDS took the drug while 60% took the plecebo.

The females who did not get AIDS are statiscally similar both at above 4600 females.  

#### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
table1 <- xtabs(~infected + treatment, data=avastf)
rowPerc(table1)
colPerc(table1)
```
On this table we can see more accurately that 31.42% of the females who got AIDS took the drug compared to the 68.58% who took the placebo.

This table also shows that 4.35% of the females of the over all who took the drug got AIDS compared to the 9.16% of females who took the placebo got the disease.

### Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
chisq.test(table1)
chisqtestGC(table1)
```
A total of 678 of the 9975 of the females in the study got the Disease. Out of those women, 213 took the drug and 465 took the placebo.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

When it comes to females, it appears that the drug did make a significant difference in preventing the women participants from being infected with AIDS. The 252 poeple difference is not enough to state a deffinitive statistical success but when you look at the fact that twice as many women got the disease while on the placebo than those on the drug, it shows there must be some success in this drug in respect to this subgroup.
 
The p-value is below 0.05 therfore we reject the null hypothesis. 

